LAGOS lake depth

### 2021-11-12 README.Rmd
add paper doi

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Data DOI](https://img.shields.io/badge/Data-10.6084/m9.figshare.12722246-blue.svg)](https://doi.org/10.6084/m9.figshare.12722246)

@@

**Stachelek J.**, P. J. Hanly, P. A., Soranno. Accepted. Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth. Inland Waters.

>>>>

[![Paper DOI](https://img.shields.io/badge/Paper-10.1080/20442041.2021.2006553-blue.svg)](https://doi.org/10.1080/20442041.2021.2006553) [![Code DOI](https://img.shields.io/badge/Code-10.5281/zenodo.5672711-blue.svg)](https://doi.org/10.5281/zenodo.5672711) [![Data DOI](https://img.shields.io/badge/Data-10.6084/m9.figshare.12722246-blue.svg)](https://doi.org/10.6084/m9.figshare.12722246)

@@

**Stachelek J.**, P. J. Hanly, P. A., Soranno. Accepted. Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth. Inland Waters. doi:10.1080/20442041.2021.2006553
